{{< var titll >}}

### 2024-07-19 presentation.qmd
sommorepres
abc

```{r}
knitr::knit_exit()
```

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
```

```{r}
knitr::knit_exit()
```

@@

::: {.column width="50%"}
Non-rigged election
```{r}
appnf[[4]]
```

@@

Rigged election using standard form
```{r}
appr1[[4]]
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(penf,3))`$
\end{equation*}

Election outome 
  - Integral `r round(polynom::integral(penf,c(0,1)),3)`
  - Counting `r round(rppnf[[1]]$desms[7,2],3)`

@@

\begin{equation*}
f(x)_{0}^{1}=`r paste0(round(per1,3))`$
\end{equation*}

Election outome
```{r, echo=F}
round(polynom::integral(per1,c(0,1)),3)
```

@@

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- basc
```
{{< include tabpar.qmd >}}

@@

### Normal form
```{r}
#| echo: false
#| output: false
apps <- rigv[[1]]
```
{{< include tab.qmd >}}

@@

### Hybrid
```{r}
#| echo: false
#| output: false
apps <- rigv[[2]]
```
{{< include tab.qmd >}}

@@

### Opposition
```{r}
#| echo: false
#| output: false
apps <- rigv[[3]]
```
{{< include tab.qmd >}}

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
# abc <- seloutput(selreport(appsn))
# abc <- seloutput(selreport(apprn))
```

@@

::: {.column width="50%"}
Non-rigged election
```{r}
#appsn[[4]]
```

@@

Rigged election using standard form
```{r}
#apprs[[4]]
```

@@

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(penf,3))`$
\end{equation*}

Election outome 
  - Integral `r #round(polynom::integral(penf,c(0,1)),3)`
  - Counting `r #round(rppnf[[1]]$desms[7,2],3)`

@@

\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(per1,3))`$
\end{equation*}

Election outome
```{r, echo=F}
#round(polynom::integral(per1,c(0,1)),3)
```

@@

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- appsn
```
{{< include tabpar.qmd >}}

@@

### Normal form
```{r}
#| echo: false
#| output: false
apps <- apprn
```
{{< include tab.qmd >}}

@@

### Hybrid
```{r}
#| echo: false
#| output: false
apps <- apprh
```
{{< include tab.qmd >}}

@@

### Opposition
```{r}
#| echo: false
#| output: false
apps <- appro
```
{{< include tab.qmd >}}
